### 2009-04-21 doc/usagereporter/aur-tech-draft.tex
Added to Usage Recorder doc

\section{Introduction}

\section{Purpose}
  metering resource usage
  record it in a database
    SGAS service used
    standard OGF Usage Records
  possibly billing
  job-level accounting
  user-based accounting
  project name

@@

>>>>

\section{Purpose}

The ARC Usage Reporter tool is a component implementing accounting
functionality in the ARC middleware. Its objective is to gather
metered resource usage data for each job and submit it to an
accounting service along with the job submitter's identity and
miscellaneous job-related metadata.

The accounting service stores the received usage data in a database,
and provides an interface for querying it.  Queries can be made by the
consumers of the accounting data, such as a billing component.  The
service itself is a third party application, separate from the
middleware distribution. The ARC Usage Reporter is currently capable
of using the logging service of the SweGrid Accounting System (SGAS),
but maintaining the possibility to enable utilizing other services
have been kept in mind during design.

Before the usage data collected from the resource manager is
submitted, it is transformed into records of job-level granularity. To
every job corresponds exactly one Grid user, therefore reports over a
time period (e.g.~an invoice) can be generated per-user, or
alternatively on a larger scale such as job project or VO level.

@@

\begin{figure}[ht]
\centering{{\scalebox{0.9}{\includegraphics{usagereporting.png}}}
\caption{\label{fig:myfigure1}Components participating in accounting.} }
\end{figure}
